Cryptographic assurance of secrecy and fairness in voting

### 2012-12-08 paper/paper.tex
Mention receipt-freeness

\term{Helios}, which is designed for use in an online setting, has no illusions about coercion: in fact,
the public implementation makes it clear to voters that they would be easy to coerce. Setting
physical security aside: as with \term{Scantegrity}, \term{Helios} does not reveal to a voter all the
information necessary to \emph{prove} a decryption of her ballot. Though a voter is able to see
encryption details for ballots chosen for audit, that information is never displayed to the user
when finally casting a ballot. Furthermore, even if it were, it is possible (though perhaps
unlikely) that a crafty voter could fashion encryption details (a false key and false randomization
data) that would produce the same hash but for a different candidate, thus convincing the coercer
of something untrue.
This is one reason that it is important for the system to use a collision-resistant hash function.

>>>>

\term{Helios}, which is designed for use in an online setting, has no illusions about coercion: in fact,
the public implementation makes it clear to voters that they would be easy to coerce. Setting
physical security aside, as with \term{Scantegrity}, \term{Helios} does not reveal to a voter all the
information necessary to \emph{prove} a decryption of her ballot, thus providing receipt-freeness. Though a voter is able to see
encryption details for ballots chosen for audit, that information is never displayed to the user
when finally casting a ballot. Furthermore, even if it were, it is possible (though perhaps
unlikely) that a crafty voter could fashion encryption details (a false key and false randomization
data) that would produce the same hash but for a different candidate, thus convincing the coercer
of something untrue.
This is one reason that it is important for the system to use a collision-resistant hash function.
